Ethereum: A Secure Decentralised Generalised Transaction Ledger \\ {\smaller \textbf{EIP-150 revision (\YellowPaperVersionNumber{})}}

### 2017-10-02 Paper.tex
Removed e with Umlaut to see if it will still build successfully.
Minor edits after l. 2086 to 2111 for build to pass.
l. 2095 to 2111 retyping in case of copy paste causing the build error.
l. 2095 to 2111 retyping and deleting unnecesary white space in case copy and paste is causing a build error, plus changing hypertarget captions (shouldn't make a difference, but just in case).

\documentclass[9pt,oneside]{amsart}
\usepackage{cancel}
%\usepackage{tweaklist}
\usepackage[utf8]{inputenc}
\DeclareUnicodeCharacter{C3}{\"{e}}
\DeclareUnicodeCharacter{AD}{\Huge [ICI]}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[a4paper,width=170mm,top=18mm,bottom=22mm,includeheadfoot]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{natbib}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{afterpage}
\usepackage{tikz}
\usepackage{underscore}
%\usepackage{lipsum} % to generate filler text for testing of document rendering
\usepackage[english]{babel}
\usepackage[autostyle]{csquotes}
\MakeOuterQuote{"}
\usepackage[bookmarks=true, unicode=true, pdftitle={Ethereum Yellow Paper: a formal specification of Ethereum, a programmable blockchain}, pdfauthor={Gavin Wood and others as per https://github.com/ethereum/yellowpaper/commits/master},pdfkeywords={Ethereum, Yellow Paper, blockchain, virtual machine, cryptography, decentralised, singleton, transaction, generalised},pdfborder={0 0 0.5 [1 3]}]{hyperref}
%,pagebackref=true

@@

\section{Ethash}\label{app:ethash}
\subsection{Definitions}
We employ the following definitions:

%\begin{tabularx}{\textwidth}{lrX}
\begin{tabu}{X[,l]X[,r]X[,l]} 
\toprule
Name & Value & Description \hypertarget{Jwordbytes}{\\
\midrule 
$J_{\mathrm{wordbytes}}$ & 4  & This is the bytes in a word.}\hypertarget{Jdatasetinit}{\\
$J_{\mathrm{datasetinit}}$ & $2^{30}$ & This is the bytes in the dataset at genesis. }\hypertarget{Jdatasetgrowth}{\\
$J_{\mathrm{datasetgrowth}}$ & $2^{23}$ & This is the dataset growth per epoch. }\hypertarget{Jcacheinit}{\\
$J_{\mathrm{cacheinit}}$ & $2^{24}$ & This is the bytes in the cache at genesis.}\hypertarget{Jcachegrowth}{\\
$J_{\mathrm{cachegrowth}}$ & $2^{17}$ & This is the cache growth per epoch.}\hypertarget{Jepoch}{\\
$J_{\mathrm{epoch}}$ & 30000 & This is the blocks per epoch.}\hypertarget{Jmixbytes}{\\
$J_{\mathrm{mixbytes}}$ & 128 & This is the mix length in bytes.}\hypertarget{Jhashbytes}{\\
$J_{\mathrm{hashbytes}}$ & 64 & This is the hash length in bytes.}\hypertarget{Jparents}{\\
$J_{\mathrm{parents}}$ & 256 & This is the number of parents of each dataset element.}\hypertarget{Jcacherounds}{\\
$J_{\mathrm{cacherounds}}$ & 3 & This is the number of rounds in cache production.}\hypertarget{Jaccesses}{\\
$J_{\mathrm{accesses}}$ & 64 & This is the number of accesses in a hashimoto loop.}\\
\bottomrule
\end{tabu}
%\end{tabularx}

>>>>

\documentclass[9pt,oneside]{amsart}
\usepackage{cancel}
%\usepackage{tweaklist}
\usepackage[utf8]{inputenc}
%This character renders, so this shouldn't be needed: \DeclareUnicodeCharacter{C3}{\"{e}}
%For testing: \DeclareUnicodeCharacter{AD}{\Huge [ICI]}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[a4paper,width=170mm,top=18mm,bottom=22mm,includeheadfoot]{geometry}
\usepackage{booktabs}
\usepackage{array}
\usepackage{verbatim}
\usepackage{caption}
\usepackage{natbib}
\usepackage{float}
\usepackage{pdflscape}
\usepackage{mathtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{afterpage}
\usepackage{tikz}
\usepackage{underscore}
%\usepackage{lipsum} % to generate filler text for testing of document rendering
\usepackage[english]{babel}
\usepackage[autostyle]{csquotes}
\MakeOuterQuote{"}
\usepackage[bookmarks=true, unicode=true, pdftitle={Ethereum Yellow Paper: a formal specification of Ethereum, a programmable blockchain}, pdfauthor={Gavin Wood and others as per https://github.com/ethereum/yellowpaper/commits/master},pdfkeywords={Ethereum, Yellow Paper, blockchain, virtual machine, cryptography, decentralised, singleton, transaction, generalised},pdfborder={0 0 0.5 [1 3]}]{hyperref}
%,pagebackref=true

@@

\section{Ethash} \label{app:ethash}
\subsection{Definitions}
We employ the following definitions:

%\begin{tabularx}{\textwidth}{lrX}
\begin{tabu}{X[,l]X[,r]X[,l]}
\toprule
Name & Value & Description \hypertarget{Jwordbytes}{}\\
\midrule
$J_{\mathrm{wordbytes}}$ & 4  & This is the bytes in a word.}\hypertarget{Jdatasetinit}{}\\
$J_{\mathrm{datasetinit}}$ & $2^{30}$ & This is the bytes in the dataset at genesis. \hypertarget{Jdatasetgrowth}{}\\
$J_{\mathrm{datasetgrowth}}$ & $2^{23}$ & This is the dataset growth per epoch. \hypertarget{Jcacheinit}{}\\
$J_{\mathrm{cacheinit}}$ & $2^{24}$ & This is the bytes in the cache at genesis.\hypertarget{Jcachegrowth}{}\\
$J_{\mathrm{cachegrowth}}$ & $2^{17}$ & This is the cache growth per epoch.\hypertarget{Jepoch}{}\\
$J_{\mathrm{epoch}}$ & 30000 & This is the blocks per epoch.\hypertarget{Jmixbytes}{}\\
$J_{\mathrm{mixbytes}}$ & 128 & This is the mix length in bytes.\hypertarget{Jhashbytes}{}\\
$J_{\mathrm{hashbytes}}$ & 64 & This is the hash length in bytes.\hypertarget{Jparents}{}\\
$J_{\mathrm{parents}}$ & 256 & This is the number of parents of each dataset element.\hypertarget{Jcacherounds}{}\\
$J_{\mathrm{cacherounds}}$ & 3 & This is the number of rounds in cache production.\hypertarget{Jaccesses}{}\\
$J_{\mathrm{accesses}}$ & 64 & This is the number of accesses in a hashimoto loop.\\
\bottomrule
\end{tabu}
%\end{tabularx}
